Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems

### 2020-11-18 paper/main.tex
update lop definition
fix suppl ref
recalculate everything after the reverts

The \emph{Linear Ordering Problem (LOP)} is defined as 
\begin{equation}\label{eq:lop}
  \min_{\sigma \in S_n} f(\sigma) = \sum_{i=1}^{n-1} \sum_{j=i+1}^n  a_{\sigma(i), \sigma(j)}
\end{equation}
where $[a_{i,j}]$ is a matrix of size $n \times n$.

@@

In the case of the PFSP, the progress of both algorithms resembles a random search, as illustrated by the results
 obtained on \texttt{rec05} (Fig.~\ref{fig:rec05}), which is the smallest PFSP
instance considered here. The lack of any apparent convergence suggests that
the models (both Bayesian and probabilistic) are not learning anything about
the fitness landscape. Results for larger PFSP corroborate these conclusions\supplement.
% \manuel{Although previous studies~\citep{ZaeStoBar2014:ppsn} concluded
% that other distance measures are more suited than Kendall's-$\tau$ distance for
% the PFSP, the reported fitness differences between various distance metrics are
% small.
% Hence, we conjecture that the same behavior will be observed with other distance metrics.}{}\MANUEL{On second thought, I'm not sure we should say this, because we really have no idea and we actually hope it is not true.}

>>>>

The \emph{Linear Ordering Problem (LOP)}, when minimizing, is defined as
%\footnote{For consistency with the other problems, we minimise the lower triangle instead of maximising the upper triangle.} 
\begin{equation}\label{eq:lop}
  \min_{\sigma \in S_n} f(\sigma) = \sum_{i=1}^{n} \sum_{j=1}^{i-1}  a_{\sigma^{-1}(i), \sigma^{-1}(j)}
\end{equation}
where $[a_{i,j}]$ is a matrix of size $n \times n$ and $\sigma^{-1}$ is the inverse of $\sigma$.

@@

In the case of the PFSP, the progress of both algorithms resembles a random search, as illustrated by the results
 obtained on \texttt{rec05} (Fig.~\ref{fig:rec05}), which is the smallest PFSP
instance considered here. The lack of any apparent convergence suggests that
the models (both Bayesian and probabilistic) are not learning anything about
the fitness landscape. Results for larger PFSP corroborate these conclusions (\supplement).
% \manuel{Although previous studies~\citep{ZaeStoBar2014:ppsn} concluded
% that other distance measures are more suited than Kendall's-$\tau$ distance for
% the PFSP, the reported fitness differences between various distance metrics are
% small.
% Hence, we conjecture that the same behavior will be observed with other distance metrics.}{}\MANUEL{On second thought, I'm not sure we should say this, because we really have no idea and we actually hope it is not true.}
